---
title: "Gal1pr-OsTIR1 AID*-3Myc library check"
subtitle: "Data: Pre-analysis and Data read-in"
author: "EG"
date: "September 06, 2023"
output: 
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
editor_options:
  chunk_output_type: console
---

```{r Knitr Setup}
#The below command can be added to the section above for a different output.
#runtime: shiny

#Setting the default knitr options for each chunk here.
#"warning" and "message" settings are set to F as the codes are pre-reviewed
#If running a new dataset, this can be changed to true to see all/any problems
#"error" is set to T so that the output is made and error checking can be done
knitr::opts_chunk$set(echo = TRUE, fig.width = 20, fig.height = 12,
                      warning = FALSE, message = FALSE, error = TRUE) 
```

```{r General Setup}
#Set working directory
setwd("~/Downloads/AID_libraries_3_AIDv2")
PrimaryDirectory = getwd()

#Load needed packages
library(tidyverse)
library(openxlsx)
library(gitter)
library(gridExtra)
library(magick)

#Set ggplot theme
theme_set(theme_light(base_size=16))
doc_theme <- theme_get()

#Loading "Alphabet" list
alphabet1536 <- c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K", "L",
                  "M", "N", "O", "P", "Q", "R", "S", "T", "U", "V", "W", "X",
                  "Y", "Z", "AA", "AB", "AC", "AD", "AE", "AF")

alphabet1536_rev <- 1:length(alphabet1536)
names(alphabet1536_rev) <- alphabet1536

#Loading the Experiment's annotation file
load("20220624_AID_anno.rda")

#Loading border colonies list
BorderColonies <- read.xlsx("BorderColoniesList.xlsx", startRow = 1, colNames = TRUE, sheet = "Sheet1")

```

```{r Data directories}
raw_img_folder <- "02_raw_photographs"
analysis_folder <- "04_analysis"
plots_folder <- "05_plots"

```


```{r Functions}
#Function for converting phenobooth images from png to jpeg
convertImages_batch <- function(filedirectory_input, sourcePattern, filedirectory_output, crop_size = NULL, brightness_val = 80){
  
  require(magick)
  
  #folders
  input_folder <- filedirectory_input
  output_folder <- filedirectory_output
  print(paste0("Input folder:", input_folder))
  print(paste0("Output folder:", output_folder))
  
  #files
  inputfilelist <- dir(input_folder, pattern = sourcePattern)
  #print(inputfilelist)
  outputfilelist <- dir(output_folder, pattern = ".jpeg")
  #print(outputfilelist)
  
  #Check if there is already files at the output folder with the expected same name.
  inputlist <- str_sub(inputfilelist, 1, -5)
  outputlist <- str_sub(outputfilelist, 1, -6)
  
  if(any(inputlist %in% outputlist)){
    userCheck <- readline("WARNING. There are files in the output folder
                          with very similar names. Files will be overwritten.
                          Proceed? (T/F)")
    if(userCheck == "F" | userCheck == "f"){
      stop("User aborted run.")
    } else if(userCheck == "T" | userCheck == "t"){} else {
        stop("Unknown command. Exiting function.")}
  }
  
  #Crop sizes
  if(!is.null(crop_size)) {
    eff_crop_size <- crop_size
    print(paste0("Crop size is user defined as:", eff_crop_size))
  } else if(is.null(crop_size)) {
    print(paste0("No crop size defined. Running based on input image size."))
  }

  #Do the conversion
  for (p in 1:length(inputfilelist)) {
    
    inputfilename <- paste(input_folder, inputfilelist[p], sep = "/")
    img <- image_read(path = inputfilename, strip = T)
    
    image_size_table <- image_info(img)
    if(is.null(crop_size)){
      image_width <- image_size_table$width
      image_height <- image_size_table$height
      print(paste("Input image has measurements of width x height:", image_width,"x", image_height))
      
      if(image_width == 2560 & image_height == 1920) {
        eff_crop_size <- "1480x990+530+420" #For 2560x1920
        
      } else if(image_width == 4128 & image_height == 3096) {
        eff_crop_size <- "2400x1600+850+680" #For 4128x3096
        
      } else if(image_width == 1280 & image_height == 960) {
      eff_crop_size <- "744x496+265+210" #For 1280x960
        
      } else {
        print(paste("Image size is not within pre-defined formats.",
                    "Please provide values for the crop size needed.",
                    "See ?image_crop.",
                    "Skipping file:", inputfilelist[p]))
      }
    }
    
    if(!is.null(eff_crop_size)) {
      img2 <- image_crop(img, eff_crop_size)
      img3 <- image_convert(img2, type = 'grayscale')
      img4 <- image_modulate(img3, brightness = brightness_val)
      
      outputfilename <- paste0(paste(output_folder, str_sub(inputfilelist[p], 1, -5), sep = "/"), ".jpeg")
      image_write(image = img4, path = outputfilename, format = "jpeg", quality = 100)
    }
    
  }
  
  #Clear memory after opening and converting large files
  ## Maybe I have to move this into the loop above instead of at the end.
  gc(verbose = FALSE)
  
}

convertImages_single <- function(filedirectory_input, filename_input, filedirectory_output, crop_size = NULL, brightness_val = 80){
  
  require(magick)
  
  #folders
  input_folder <- filedirectory_input
  output_folder <- filedirectory_output
  print(paste0("Input folder:", input_folder))
  print(paste0("Output folder:", output_folder))
  
  #files
  outputfilelist <- dir(output_folder, pattern = ".jpeg")
  
  #Check if there is already files at the output folder with the expected same name.
  inputlist <- str_sub(filename_input, 1, -5)
  outputlist <- str_sub(outputfilelist, 1, -6)
  
  if(any(inputlist %in% outputlist)){
    userCheck <- readline("WARNING. There are files in the output folder
                          with very similar names. Files will be overwritten.
                          Proceed? (T/F)")
    if(userCheck == "F" | userCheck == "f"){
      stop("User aborted run.")
    } else if(userCheck == "T" | userCheck == "t"){} else {
        stop("Unknown command. Exiting function.")}
  }
  
  #Crop sizes
  if(!is.null(crop_size)) {
    eff_crop_size <- crop_size
    print(paste0("Crop size is user defined as:", eff_crop_size))
  } else if(is.null(crop_size)) {
    print(paste0("No crop size defined. Running based on input image size."))
  }

  #Do the conversion
  inputfilename <- paste(input_folder, filename_input, sep = "/")
  img <- image_read(path = inputfilename, strip = T)
  
  image_size_table <- image_info(img)
  if(is.null(crop_size)){
    image_width <- image_size_table$width
    image_height <- image_size_table$height
    print(paste("Input image has measurements of width x height:", image_width,"x", image_height))
    
    if(image_width == 2560 & image_height == 1920) {
      eff_crop_size <- "1480x990+530+420" #For 2560x1920
      
    } else if(image_width == 4128 & image_height == 3096) {
      eff_crop_size <- "2400x1600+850+680" #For 4128x3096
      
    } else if(image_width == 1280 & image_height == 960) {
      eff_crop_size <- "744x496+265+210" #For 1280x960
      
    } else {
      gc(verbose = FALSE)
      stop(paste("Image size is not within pre-defined formats.",
                  "Please provide values for the crop size needed.",
                  "See ?image_crop.",
                  "Skipping file:", filename_input))
    }
  }
  
  img2 <- image_crop(img, eff_crop_size)
  img3 <- image_convert(img2, type = 'grayscale')
  img4 <- image_modulate(img3, brightness = brightness_val)
  
  outputfilename <- paste0(paste(output_folder, str_sub(filename_input, 1, -5), sep = "/"), ".jpeg")
  image_write(image = img4, path = outputfilename, format = "jpeg", quality = 100)
  
  
  #Clear memory after opening and converting large files
  ## Maybe I have to move this into the loop above instead of at the end.
  gc(verbose = FALSE)
  
}

```

This document contains the workflow for read-in of phenobooth images of the AID library check performed. The strains that were produced after crossing the C-SWAT library with the AID tag donor strain. The AID library strain is then pinned onto agar with IAA to induce the degron. This experiments has 4 different replicates.

# Image data

## Photograph Segmentation

```{r photoseg, include = FALSE, eval = FALSE}
#Segment hygromycin selection photographs
raw_img_folder_Hyg <- paste(PrimaryDirectory, raw_img_folder, "20230801_Hyg_Selection2_AID-3Myc/Images", sep = "/")
analysis_folder_Hyg <- paste(PrimaryDirectory, analysis_folder, "20230801_Hyg_Selection2_AID-3Myc", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_Hyg, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_Hyg, brightness_val = 50)

#head(dir(analysis_folder_Hyg, pattern=".jpeg"))
setwd(analysis_folder_Hyg)
gitter.batch(analysis_folder_Hyg, plate.format=384, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_Hyg, dat.save=analysis_folder_Hyg)

#setwd(analysis_folder_Hyg)
nPlates <- 24
photoNamesHyg <- dir(analysis_folder_Hyg, pattern = "jpeg.dat")
photoDataHyg <- data.frame()
for (i in 1:nPlates) {
  photoHyg <- gitter.read(photoNamesHyg[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataHyg <- bind_rows(photoDataHyg, photoHyg)
}
names(photoDataHyg)[3:4] <- c("sizeHyg","circularityHyg")
setwd(PrimaryDirectory)
save(photoDataHyg, file = "photoData_Hyg.rda")



#Segment ctrl day 1 photographs 
raw_img_folder_ctrl_d1 <- paste(PrimaryDirectory, raw_img_folder, "20230818_Gal1_Screen_control", sep = "/")
analysis_folder_ctrl_d1 <- paste(PrimaryDirectory, analysis_folder, "20230818_Gal1_Screen_control", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_ctrl_d1, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_ctrl_d1, brightness_val = 65)

#head(dir(analysis_folder_ctrl_d1, pattern=".jpeg"))
setwd(analysis_folder_ctrl_d1)
gitter.batch(analysis_folder_ctrl_d1, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_ctrl_d1, dat.save=analysis_folder_ctrl_d1)

#setwd(analysis_folder_ctrl_d1)
nPlates <- 24
photoNamesctrl_d1 <- dir(analysis_folder_ctrl_d1, pattern = "jpeg.dat")
photoDatactrl_d1 <- data.frame()
for (i in 1:nPlates) {
  photoctrl_d1 <- gitter.read(photoNamesctrl_d1[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDatactrl_d1 <- bind_rows(photoDatactrl_d1, photoctrl_d1)
}
names(photoDatactrl_d1)[3:4] <- c("sizectrl_d1","circularityctrl_d1")
setwd(PrimaryDirectory)
save(photoDatactrl_d1, file = "photoData_ctrl_d1.rda")

#SEE WITH JOHN; IMAGE NUMBER 4 IS NOT READING 


#Segment ctrl day 2 photographs 
raw_img_folder_ctrl_d2 <- paste(PrimaryDirectory, raw_img_folder, "20230819_Gal1_Screen_control", sep = "/")
analysis_folder_ctrl_d2 <- paste(PrimaryDirectory, analysis_folder, "20230819_Gal1_Screen_control", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_ctrl_d2, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_ctrl_d2, brightness_val = 65)

#head(dir(analysis_folder_ctrl_d2, pattern=".jpeg"))
setwd(analysis_folder_ctrl_d2)
gitter.batch(analysis_folder_ctrl_d2, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_ctrl_d2, dat.save=analysis_folder_ctrl_d2)

#setwd(analysis_folder_ctrl_d2)
nPlates <- 24
photoNamesctrl_d2 <- dir(analysis_folder_ctrl_d2, pattern = "jpeg.dat")
photoDatactrl_d2 <- data.frame()
for (i in 1:nPlates) {
  photoctrl_d2 <- gitter.read(photoNamesctrl_d2[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDatactrl_d2 <- bind_rows(photoDatactrl_d2, photoctrl_d2)
}
names(photoDatactrl_d2)[3:4] <- c("sizectrl_d2","circularityctrl_d2")
setwd(PrimaryDirectory)
save(photoDatactrl_d2, file = "photoData_ctrl_d2.rda")





#Segment 1um IAA day 1 photographs
raw_img_folder_IAA_d1 <- paste(PrimaryDirectory, raw_img_folder, "20230818_Gal1_Screen_IAA/Images", sep = "/")
analysis_folder_IAA_d1 <- paste(PrimaryDirectory, analysis_folder, "20230818_Gal1_Screen_IAA", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_IAA_d1, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_IAA_d1, brightness_val = 65)

#head(dir(analysis_folder_IAA_d1, pattern=".jpeg"))
setwd(analysis_folder_IAA_d1)
gitter.batch(analysis_folder_IAA_d1, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_IAA_d1, dat.save=analysis_folder_IAA_d1)

#setwd(analysis_folder_IAA_d1)
nPlates <- 24
photoNamesIAA_d1 <- dir(analysis_folder_IAA_d1, pattern = "jpeg.dat")
photoDataIAA_d1 <- data.frame()
for (i in 1:nPlates) {
  photoIAA_d1 <- gitter.read(photoNamesIAA_d1[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataIAA_d1 <- bind_rows(photoDataIAA_d1, photoIAA_d1)
}
names(photoDataIAA_d1)[3:4] <- c("sizeIAA_d1","circularityIAA_d1")
setwd(PrimaryDirectory)
save(photoDataIAA_d1, file = "photoData_IAA_d1.rda")



#Segment 1um IAA day 2 photographs
raw_img_folder_IAA_d2 <- paste(PrimaryDirectory, raw_img_folder, "20230819_Gal1_Screen_IAA/Images", sep = "/")
analysis_folder_IAA_d2 <- paste(PrimaryDirectory, analysis_folder, "20230819_Gal1_Screen_IAA", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_IAA_d2, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_IAA_d2, brightness_val = 65)

#head(dir(analysis_folder_IAA_d2, pattern=".jpeg"))
setwd(analysis_folder_IAA_d2)
gitter.batch(analysis_folder_IAA_d2, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_IAA_d2, dat.save=analysis_folder_IAA_d2)

#setwd(analysis_folder_IAA_d2)
nPlates <- 24
photoNamesIAA_d2 <- dir(analysis_folder_IAA_d2, pattern = "jpeg.dat")
photoDataIAA_d2 <- data.frame()
for (i in 1:nPlates) {
  photoIAA_d2 <- gitter.read(photoNamesIAA_d2[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataIAA_d2 <- bind_rows(photoDataIAA_d2, photoIAA_d2)
}
names(photoDataIAA_d2)[3:4] <- c("sizeIAA_d2","circularityIAA_d2")
setwd(PrimaryDirectory)
save(photoDataIAA_d2, file = "photoData_IAA_d2.rda")



#Segment CPT day 1  photographs
raw_img_folder_CPT_d1 <- paste(PrimaryDirectory, raw_img_folder, "20230818_Gal1_Screen_IAA_CPT/Images", sep = "/")
analysis_folder_CPT_d1 <- paste(PrimaryDirectory, analysis_folder, "20230818_Gal1_Screen_IAA_CPT", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_CPT_d1, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_CPT_d1, brightness_val = 65)

#head(dir(analysis_folder_CPT_d1, pattern=".jpeg"))
setwd(analysis_folder_CPT_d1)
gitter.batch(analysis_folder_CPT_d1, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_CPT_d1, dat.save=analysis_folder_CPT_d1)

#setwd(analysis_folder_CPT_d1)
nPlates <- 24
photoNamesCPT_d1 <- dir(analysis_folder_CPT_d1, pattern = "jpeg.dat")
photoDataCPT_d1 <- data.frame()
for (i in 1:nPlates) {
  photoCPT_d1 <- gitter.read(photoNamesCPT_d1[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataCPT_d1 <- bind_rows(photoDataCPT_d1, photoCPT_d1)
}
names(photoDataCPT_d1)[3:4] <- c("sizeCPT_d1","circularityCPT_d1")
setwd(PrimaryDirectory)
save(photoDataCPT_d1, file = "photoData_CPT_d1.rda")



#Segment CPT day 2  photographs
raw_img_folder_CPT_d2 <- paste(PrimaryDirectory, raw_img_folder, "20230819_Gal1_Screen_IAA_CPT/Images", sep = "/")
analysis_folder_CPT_d2 <- paste(PrimaryDirectory, analysis_folder, "20230819_Gal1_Screen_IAA_CPT", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_CPT_d2, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_CPT_d2, brightness_val = 65)

#head(dir(analysis_folder_CPT_d2, pattern=".jpeg"))
setwd(analysis_folder_CPT_d2)
gitter.batch(analysis_folder_CPT_d2, plate.format=1536, verbose="p", contrast = 1E-100, remove.noise = T,
             grid.save=analysis_folder_CPT_d2, dat.save=analysis_folder_CPT_d2)

#setwd(analysis_folder_CPT_d2)
nPlates <- 24
photoNamesCPT_d2 <- dir(analysis_folder_CPT_d2, pattern = "jpeg.dat")
photoDataCPT_d2 <- data.frame()
for (i in 1:nPlates) {
  photoCPT_d2 <- gitter.read(photoNamesCPT_d2[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataCPT_d2 <- bind_rows(photoDataCPT_d2, photoCPT_d2)
}
names(photoDataCPT_d2)[3:4] <- c("sizeCPT_d2","circularityCPT_d2")
setwd(PrimaryDirectory)
save(photoDataCPT_d2, file = "photoData_CPT_d2.rda")

#Could not run the gitter in all of them - I will not use them




#Segment CPT_IAA day 1 photographs
raw_img_folder_CPT_IAA_d1 <- paste(PrimaryDirectory, raw_img_folder, "20230818_Gal1_Screen_IAA_CPT_IAA", sep = "/")
analysis_folder_CPT_IAA_d1 <- paste(PrimaryDirectory, analysis_folder, "20230818_Gal1_Screen_IAA_CPT_IAA", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_CPT_IAA_d1, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_CPT_IAA_d1, brightness_val = 65)

#head(dir(analysis_folder_CPT_IAA_d1, pattern=".jpeg"))
setwd(analysis_folder_CPT_IAA_d1)
gitter.batch(analysis_folder_CPT_IAA_d1, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_CPT_IAA_d1, dat.save=analysis_folder_CPT_IAA_d1)

#setwd(analysis_folder_CPT_IAA_d1)
nPlates <- 24
photoNamesCPT_IAA_d1 <- dir(analysis_folder_CPT_IAA_d1, pattern = "jpeg.dat")
photoDataCPT_IAA_d1 <- data.frame()
for (i in 1:nPlates) {
  photoCPT_IAA_d1 <- gitter.read(photoNamesCPT_IAA_d1[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataCPT_IAA_d1 <- bind_rows(photoDataCPT_IAA_d1, photoCPT_IAA_d1)
}
names(photoDataCPT_IAA_d1)[3:4] <- c("sizeCPT_IAA_d1","circularityCPT_IAA_d1")
setwd(PrimaryDirectory)
save(photoDataCPT_IAA_d1, file = "photoData_CPT_IAA_d1.rda")




#Segment CPT_IAA day 2 photographs
raw_img_folder_CPT_IAA_d2 <- paste(PrimaryDirectory, raw_img_folder, "20230819_Gal1_Screen_IAA_CPT_IAA", sep = "/")
analysis_folder_CPT_IAA_d2 <- paste(PrimaryDirectory, analysis_folder, "20230819_Gal1_Screen_IAA_CPT_IAA", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_CPT_IAA_d2, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_CPT_IAA_d2, brightness_val = 65)

#head(dir(analysis_folder_CPT_IAA_d2, pattern=".jpeg"))
setwd(analysis_folder_CPT_IAA_d2)
gitter.batch(analysis_folder_CPT_IAA_d2, plate.format=1536, verbose="p", contrast = 1E-100, remove.noise = T,
             grid.save=analysis_folder_CPT_IAA_d2, dat.save=analysis_folder_CPT_IAA_d2)

#setwd(analysis_folder_CPT_IAA_d1)
nPlates <- 24
photoNamesCPT_IAA_d2 <- dir(analysis_folder_CPT_IAA_d2, pattern = "jpeg.dat")
photoDataCPT_IAA_d2 <- data.frame()
for (i in 1:nPlates) {
  photoCPT_IAA_d2 <- gitter.read(photoNamesCPT_IAA_d2[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataCPT_IAA_d2 <- bind_rows(photoDataCPT_IAA_d2, photoCPT_IAA_d2)
}
names(photoDataCPT_IAA_d2)[3:4] <- c("sizeCPT_IAA_d2","circularityCPT_IAA_d2")
setwd(PrimaryDirectory)
save(photoDataCPT_IAA_d2, file = "photoData_CPT_IAA_d2.rda")

#Could not run the gitter in all of them - I will not use them



#Segment HU day 1 photographs
raw_img_folder_HU_d1 <- paste(PrimaryDirectory, raw_img_folder, "20230818_Gal1_Screen_IAA_HU/Images", sep = "/")
analysis_folder_HU_d1 <- paste(PrimaryDirectory, analysis_folder, "20230818_Gal1_Screen_IAA_HU", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_HU_d1, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_HU_d1, brightness_val = 65)

#head(dir(analysis_folder_HU_d1, pattern=".jpeg"))
setwd(analysis_folder_HU_d1)
gitter.batch(analysis_folder_HU_d1, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_HU_d1, dat.save=analysis_folder_HU_d1)

#setwd(analysis_folder_HU_d1)
nPlates <- 24
photoNamesHU_d1 <- dir(analysis_folder_HU_d1, pattern = "jpeg.dat")
photoDataHU_d1 <- data.frame()
for (i in 1:nPlates) {
  photoHU_d1 <- gitter.read(photoNamesHU_d1[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataHU_d1 <- bind_rows(photoDataHU_d1, photoHU_d1)
}
names(photoDataHU_d1)[3:4] <- c("sizeHU_d1","circularityHU_d1")
setwd(PrimaryDirectory)
save(photoDataHU_d1, file = "photoData_HU_d1.rda")




#Segment HU day 2 photographs
raw_img_folder_HU_d2 <- paste(PrimaryDirectory, raw_img_folder, "20230819_Gal1_Screen_IAA_HU/Images", sep = "/")
analysis_folder_HU_d2 <- paste(PrimaryDirectory, analysis_folder, "20230819_Gal1_Screen_IAA_HU", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_HU_d2, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_HU_d2, brightness_val = 65)

#head(dir(analysis_folder_HU_d2, pattern=".jpeg"))
setwd(analysis_folder_HU_d2)
gitter.batch(analysis_folder_HU_d2, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_HU_d2, dat.save=analysis_folder_HU_d2)

#setwd(analysis_folder_HU_d2)
nPlates <- 24
photoNamesHU_d2 <- dir(analysis_folder_HU_d2, pattern = "jpeg.dat")
photoDataHU_d2 <- data.frame()
for (i in 1:nPlates) {
  photoHU_d2 <- gitter.read(photoNamesHU_d2[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataHU_d2 <- bind_rows(photoDataHU_d2, photoHU_d2)
}
names(photoDataHU_d2)[3:4] <- c("sizeHU_d2","circularityHU_d2")
setwd(PrimaryDirectory)
save(photoDataHU_d2, file = "photoData_HU_d2.rda")



#Segment HU_IAA day 1 photographs
raw_img_folder_HU_IAA_d1 <- paste(PrimaryDirectory, raw_img_folder, "20230818_Gal1_Screen_IAA_HU_IAA", sep = "/")
analysis_folder_HU_IAA_d1 <- paste(PrimaryDirectory, analysis_folder, "20230818_Gal1_Screen_IAA_HU_IAA", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_HU_IAA_d1, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_HU_IAA_d1, brightness_val = 65)

#head(dir(analysis_folder_HU_IAA_d1, pattern=".jpeg"))
setwd(analysis_folder_HU_IAA_d1)
gitter.batch(analysis_folder_HU_IAA_d1, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_HU_IAA_d1, dat.save=analysis_folder_HU_IAA_d1)

#setwd(analysis_folder_HU_IAA_d1)
nPlates <- 24
photoNamesHU_IAA_d1 <- dir(analysis_folder_HU_IAA_d1, pattern = "jpeg.dat")
photoDataHU_IAA_d1 <- data.frame()
for (i in 1:nPlates) {
  photoHU_IAA_d1 <- gitter.read(photoNamesHU_IAA_d1[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataHU_IAA_d1 <- bind_rows(photoDataHU_IAA_d1, photoHU_IAA_d1)
}
names(photoDataHU_IAA_d1)[3:4] <- c("sizeHU_IAA_d1","circularityHU_IAA_d1")
setwd(PrimaryDirectory)
save(photoDataHU_IAA_d1, file = "photoData_HU_IAA_d1.rda")



#Segment HU_IAA day 2 photographs
raw_img_folder_HU_IAA_d2 <- paste(PrimaryDirectory, raw_img_folder, "20230819_Gal1_Screen_IAA_HU_IAA", sep = "/")
analysis_folder_HU_IAA_d2 <- paste(PrimaryDirectory, analysis_folder, "20230819_Gal1_Screen_IAA_HU_IAA", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_HU_IAA_d2, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_HU_IAA_d2, brightness_val = 65)

#head(dir(analysis_folder_HU_IAA_d2, pattern=".jpeg"))
setwd(analysis_folder_HU_IAA_d2)
gitter.batch(analysis_folder_HU_IAA_d2, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_HU_IAA_d2, dat.save=analysis_folder_HU_IAA_d2)

#setwd(analysis_folder_HU_IAA_d2)
nPlates <- 24
photoNamesHU_IAA_d2 <- dir(analysis_folder_HU_IAA_d2, pattern = "jpeg.dat")
photoDataHU_IAA_d2 <- data.frame()
for (i in 1:nPlates) {
  photoHU_IAA_d2 <- gitter.read(photoNamesHU_IAA_d2[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataHU_IAA_d2 <- bind_rows(photoDataHU_IAA_d2, photoHU_IAA_d2)
}
names(photoDataHU_IAA_d2)[3:4] <- c("sizeHU_IAA_d2","circularityHU_IAA_d2")
setwd(PrimaryDirectory)
save(photoDataHU_IAA_d2, file = "photoData_HU_IAA_d2.rda")



#Segment MMS day 1 photographs
raw_img_folder_MMS_d1 <- paste(PrimaryDirectory, raw_img_folder, "20230818_Gal1_Screen_IAA_MMS/Images", sep = "/")
analysis_folder_MMS_d1 <- paste(PrimaryDirectory, analysis_folder, "20230818_Gal1_Screen_IAA_MMS", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_MMS_d1, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_MMS_d1, brightness_val = 65)

#head(dir(analysis_folder_MMS_d1, pattern=".jpeg"))
setwd(analysis_folder_MMS_d1)
gitter.batch(analysis_folder_MMS_d1, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_MMS_d1, dat.save=analysis_folder_MMS_d1)

#setwd(analysis_folder_MMS_d1)
nPlates <- 24
photoNamesMMS_d1 <- dir(analysis_folder_MMS_d1, pattern = "jpeg.dat")
photoDataMMS_d1 <- data.frame()
for (i in 1:nPlates) {
  photoMMS_d1 <- gitter.read(photoNamesMMS_d1[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataMMS_d1 <- bind_rows(photoDataMMS_d1, photoMMS_d1)
}
names(photoDataMMS_d1)[3:4] <- c("sizeMMS_d1","circularityMMS_d1")
setwd(PrimaryDirectory)
save(photoDataMMS_d1, file = "photoData_MMS_d1.rda")



#Segment MMS day 2 photographs
raw_img_folder_MMS_d2 <- paste(PrimaryDirectory, raw_img_folder, "20230819_Gal1_Screen_IAA_MMS/Images", sep = "/")
analysis_folder_MMS_d2 <- paste(PrimaryDirectory, analysis_folder, "20230819_Gal1_Screen_IAA_MMS", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_MMS_d2, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_MMS_d2, brightness_val = 65)

#head(dir(analysis_folder_MMS_d2, pattern=".jpeg"))
setwd(analysis_folder_MMS_d2)
gitter.batch(analysis_folder_MMS_d2, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_MMS_d2, dat.save=analysis_folder_MMS_d2)

#setwd(analysis_folder_MMS_d2)
nPlates <- 24
photoNamesMMS_d2 <- dir(analysis_folder_MMS_d2, pattern = "jpeg.dat")
photoDataMMS_d2 <- data.frame()
for (i in 1:nPlates) {
  photoMMS_d2 <- gitter.read(photoNamesMMS_d2[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataMMS_d2 <- bind_rows(photoDataMMS_d2, photoMMS_d2)
}
names(photoDataMMS_d2)[3:4] <- c("sizeMMS_d2","circularityMMS_d2")
setwd(PrimaryDirectory)
save(photoDataMMS_d2, file = "photoData_MMS_d2.rda")



#Segment MMS_IAA day 1 photographs
raw_img_folder_MMS_IAA_d1 <- paste(PrimaryDirectory, raw_img_folder, "20230818_Gal1_Screen_IAA_MMS_IAA", sep = "/")
analysis_folder_MMS_IAA_d1 <- paste(PrimaryDirectory, analysis_folder, "20230818_Gal1_Screen_IAA_MMS_IAA", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_MMS_IAA_d1, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_MMS_IAA_d1, brightness_val = 65)

#head(dir(analysis_folder_MMS_IAA_d1, pattern=".jpeg"))
setwd(analysis_folder_MMS_IAA_d1)
gitter.batch(analysis_folder_MMS_IAA_d1, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_MMS_IAA_d1, dat.save=analysis_folder_MMS_IAA_d1)

#setwd(analysis_folder_MMS_IAA_d1)
nPlates <- 24
photoNamesMMS_IAA_d1 <- dir(analysis_folder_MMS_IAA_d1, pattern = "jpeg.dat")
photoDataMMS_IAA_d1 <- data.frame()
for (i in 1:nPlates) {
  photoMMS_IAA_d1 <- gitter.read(photoNamesMMS_IAA_d1[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataMMS_IAA_d1 <- bind_rows(photoDataMMS_IAA_d1, photoMMS_IAA_d1)
}
names(photoDataMMS_IAA_d1)[3:4] <- c("sizeMMS_IAA_d1","circularityMMS_IAA_d1")
setwd(PrimaryDirectory)
save(photoDataMMS_IAA_d1, file = "photoData_MMS_IAA_d1.rda")



#Segment MMS_IAA day 2 photographs
raw_img_folder_MMS_IAA_d2 <- paste(PrimaryDirectory, raw_img_folder, "20230819_Gal1_Screen_IAA_MMS_IAA", sep = "/")
analysis_folder_MMS_IAA_d2 <- paste(PrimaryDirectory, analysis_folder, "20230819_Gal1_Screen_IAA_MMS_IAA", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_MMS_IAA_d2, sourcePattern = ".png",
                    filedirectory_output = analysis_folder_MMS_IAA_d2, brightness_val = 65)

#head(dir(analysis_folder_MMS_IAA_d2, pattern=".jpeg"))
setwd(analysis_folder_MMS_IAA_d2)
gitter.batch(analysis_folder_MMS_IAA_d2, plate.format=1536, verbose="p", contrast = 100, remove.noise = T,
             grid.save=analysis_folder_MMS_IAA_d2, dat.save=analysis_folder_MMS_IAA_d2)

#setwd(analysis_folder_MMS_IAA_d2)
nPlates <- 24
photoNamesMMS_IAA_d2 <- dir(analysis_folder_MMS_IAA_d2, pattern = "jpeg.dat")
photoDataMMS_IAA_d2 <- data.frame()
for (i in 1:nPlates) {
  photoMMS_IAA_d2 <- gitter.read(photoNamesMMS_IAA_d2[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataMMS_IAA_d2 <- bind_rows(photoDataMMS_IAA_d2, photoMMS_IAA_d2)
}
names(photoDataMMS_IAA_d2)[3:4] <- c("sizeMMS_IAA_d2","circularityMMS_IAA_d2")
setwd(PrimaryDirectory)
save(photoDataMMS_IAA_d2, file = "photoData_MMS_IAA_d2.rda")


```

```{r Combine photodata}
photoDataHyg$well <- paste0(photoDataHyg$row1536, sprintf("%02d", photoDataHyg$col))

photoDatactrl_d1$well <- paste0(photoDatactrl_d1$row1536, sprintf("%02d", photoDatactrl_d1$col))
photoDatactrl_d2$well <- paste0(photoDatactrl_d2$row1536, sprintf("%02d", photoDatactrl_d2$col))

photoDataIAA_d1$well <- paste0(photoDataIAA_d1$row1536, sprintf("%02d", photoDataIAA_d1$col))
photoDataIAA_d2$well <- paste0(photoDataIAA_d2$row1536, sprintf("%02d", photoDataIAA_d2$col))

photoDataCPT_d1$well <- paste0(photoDataCPT_d1$row1536, sprintf("%02d", photoDataCPT_d1$col))
#photoDataCPT_d2$well <- paste0(photoDataCPT_d2$row1536, sprintf("%02d", photoDataCPT_d2$col))

photoDataCPT_IAA_d1$well <- paste0(photoDataCPT_IAA_d1$row1536, sprintf("%02d", photoDataCPT_IAA_d1$col))
#photoDataCPT_IAA_d2$well <- paste0(photoDataCPT_IAA_d2$row1536, sprintf("%02d", photoDataCPT_IAA_d2$col))

photoDataHU_d1$well <- paste0(photoDataHU_d1$row1536, sprintf("%02d", photoDataHU_d1$col))
photoDataHU_d2$well <- paste0(photoDataHU_d2$row1536, sprintf("%02d", photoDataHU_d2$col))

photoDataHU_IAA_d1$well <- paste0(photoDataHU_IAA_d1$row1536, sprintf("%02d", photoDataHU_IAA_d1$col))
photoDataHU_IAA_d2$well <- paste0(photoDataHU_IAA_d2$row1536, sprintf("%02d", photoDataHU_IAA_d2$col))

photoDataMMS_d1$well <- paste0(photoDataMMS_d1$row1536, sprintf("%02d", photoDataMMS_d1$col))
photoDataMMS_d2$well <- paste0(photoDataMMS_d2$row1536, sprintf("%02d", photoDataMMS_d2$col))

photoDataMMS_IAA_d1$well <- paste0(photoDataMMS_IAA_d1$row1536, sprintf("%02d", photoDataMMS_IAA_d1$col))
photoDataMMS_IAA_d2$well <- paste0(photoDataMMS_IAA_d2$row1536, sprintf("%02d", photoDataMMS_IAA_d2$col))

AID_anno$well <- paste0(AID_anno$row_1536, sprintf("%02d", AID_anno$col_1536))
AID_anno$plate <- paste0("p", sprintf("%02d", AID_anno$plate_1536))

df_temp1 <- left_join(AID_anno, photoDataHyg %>% select(plate, col, row1536, sizeHyg, circularityHyg), by = c("plate", "col_384" = "col", "row_384" = "row1536"))

df_temp2 <- left_join(df_temp1, photoDatactrl_d1 %>% select(sizectrl_d1, circularityctrl_d1, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDatactrl_d2 %>% select(sizectrl_d2, circularityctrl_d2, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataIAA_d1 %>% select(sizeIAA_d1, circularityIAA_d1, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataIAA_d2 %>% select(sizeIAA_d2, circularityIAA_d2, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataCPT_d1 %>% select(sizeCPT_d1, circularityCPT_d1, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataCPT_IAA_d1 %>% select(sizeCPT_IAA_d1, circularityCPT_IAA_d1, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataHU_d1 %>% select(sizeHU_d1, circularityHU_d1, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataHU_d2 %>% select(sizeHU_d2, circularityHU_d2, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataHU_IAA_d1 %>% select(sizeHU_IAA_d1, circularityHU_IAA_d1, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataHU_IAA_d2 %>% select(sizeHU_IAA_d2, circularityHU_IAA_d2, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataMMS_d1 %>% select(sizeMMS_d1, circularityMMS_d1, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataMMS_d2 %>% select(sizeMMS_d2, circularityMMS_d2, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataMMS_IAA_d1 %>% select(sizeMMS_IAA_d1, circularityMMS_IAA_d1, plate, well), by = c("plate", "well")) %>%
  left_join(., photoDataMMS_IAA_d2 %>% select(sizeMMS_IAA_d2, circularityMMS_IAA_d2, plate, well), by = c("plate", "well")) 

# Combine data frame with annotation file
df <- df_temp2

save(df, file = "dataTableRaw.rda")

```

```{r Quick check}
ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeHyg))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeHyg), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizectrl_d1))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizectrl_d1), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizectrl_d2))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizectrl_d2), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeIAA_d1))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeIAA_d1), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeIAA_d2))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeIAA_d2), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeCPT_d1))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeCPT_d1), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeCPT_IAA_d1))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeCPT_IAA_d1), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeHU_d1))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeHU_d1), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeHU_d2))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeHU_d2), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeHU_IAA_d1))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeHU_IAA_d1), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeHU_IAA_d2))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeHU_IAA_d2), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeMMS_d1))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeMMS_d1), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeMMS_d2))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeMMS_d2), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeMMS_IAA_d1))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeMMS_IAA_d1), bins = 200)

ggplot() +
  #geom_boxplot(data = df, aes(as.factor(plate), sizeMMS_IAA_d1))
  geom_histogram(data = anti_join(df, BorderColonies), aes(sizeMMS_IAA_d2), bins = 200)

```


# R Studio Session Info

```{r Session info}
sessionInfo()

```