---
title: "Gal1-OsTIR1(F74G) mNG-AID-3Myc experiment"
subtitle: "Data: Pre-analysis and Data read-in for measurements"
author: "EG"
date: "September 04, 2023"
output: 
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
editor_options:
  chunk_output_type: console
---

```{r Knitr Setup}
#The below command can be added to the section above for a different output.
#runtime: shiny

#Setting the default knitr options for each chunk here.
#"warning" and "message" settings are set to F as the codes are pre-reviewed
#If running a new dataset, this can be changed to true to see all/any problems
#"error" is set to T so that the output is made and error checking can be done
knitr::opts_chunk$set(echo = TRUE, fig.width = 20, fig.height = 12,
                      warning = FALSE, message = FALSE, error = TRUE) 
```

```{r General Setup}
#Set working directory
setwd("~/Downloads/AID_libraries_2_AIDv1")
PrimaryDirectory = getwd()

#Load needed packages
library(tidyverse)
library(openxlsx)
library(gitter)
library(gridExtra)
library(magick)

#Set ggplot theme
theme_set(theme_light(base_size=20))
doc_theme <- theme_get()

#Loading "Alphabet" list
alphabet1536 <- c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K", "L",
                  "M", "N", "O", "P", "Q", "R", "S", "T", "U", "V", "W", "X",
                  "Y", "Z", "AA", "AB", "AC", "AD", "AE", "AF")

alphabet1536_rev <- 1:length(alphabet1536)
names(alphabet1536_rev) <- alphabet1536

#Loading the Experiment's annotation file
load("20230904_mNG_AID_anno.rda")

mNG_AID_anno <- mNG_AID_anno %>%
  mutate(well = paste0(mNG_AID_anno$row_1536, sprintf("%02d", mNG_AID_anno$col_1536)),
         plate = paste0("p", sprintf("%02d", mNG_AID_anno$plate_1536)))

#Loading border colonies list
BorderColonies <- read.xlsx("06_datasets/BorderColoniesList.xlsx", startRow = 1, colNames = TRUE, sheet = "Sheet1")

```

```{r Data directories}
raw_img_folder <- "02_raw_photographs"
raw_xlsx_folder <- "03_raw_plate_reader"
analysis_folder <- "04_analysis"
plots_folder <- "05_plots"
dataset_folder <- "06_datasets"

```


```{r Functions}
#Function for reading in excel files.
Read_Screen_Data <- function(filename, filedirectory, channels, nplate, alternate_start = 0){
  
  #filename: name of the excel workbook with all the measurements
  #filedirectory: the directory where the file is located
  #channels: a vector of character strings specifying the channel labels
  #nplate: number of plates within the file / to be imported
  #alternate_start: if the first plate in the excel file is actually not the true plate 1, then a number can be given to indicate the first plate
  
  require(tidyverse)
  require(openxlsx)
  
  #### Checks ####
  #Check file is present.
  filepath <- paste0(filedirectory,"/",filename)
  
  if(file.exists(filepath)){
    print(paste("File given exists. Proceed to import."))
  } else {
    #print(paste("This file path does not exists:", filepath))
    stop("File does not exists. Please check. ",
         "Information given: ", filepath) }
  
  #Check if nplate is an integer.
  if(nplate != round(nplate)){ stop("nplate must be an integer") }
  
  #Check if there is at least 1 channel given.
  if(length(channels) == 0){ stop("There must be at least one channel to import") }
  
  #Check if alternate_start is an integer if another number is given.
  if(alternate_start != round(alternate_start)){ stop("alternate_start must be an integer") }
  
  
  #### Processing - General ####
  #Get all the names of the sheets present in the file
  sheetNames <- getSheetNames(file = filepath)
  
  #Get all the names of the channels to be imported
  channellist <- channels
  
  #Decide how to proceed with number of sheets/plates to import
  if(length(sheetNames) != nplate){
    print(paste("WARNING. The number of sheets in Excel file does not match number of plates given."))
    print(paste("Number of plates given:", nplate))
    print(paste("Number of sheets present:", length(sheetNames)))
    
    #Check with user if they are sure with this incorrect number of plates
    userCheck <- readline("WARNING. Proceed? (T/F)")
    if(userCheck == "F" | userCheck == "f"){
      stop("User aborted run. Please check number of plates given and number sheets in Excel file.")
    } else if(userCheck == "T" | userCheck == "t"){} else {
        stop("Unknown command. Exiting function.")}
    
  }
  
  if(length(sheetNames) > nplate){
    ## This is in case the user would want to import only a subset of plates (although has to be from plate 1)
    print(paste("User chooses to import only", nplate, "sheets out of", length(sheetNames), "sheets."))
    print(paste("NOTE: Import starts from plate 1."))
    
    #Number of plates/sheets to process
    chosenNumber <- as.integer(nplate)
    
  } else if(length(sheetNames) < nplate){
    ## If the user puts nplate more than number of sheets, the code will just import what is possible.
    print(paste("User input more plates than sheets available."))
    print(paste("Proceeding with what is possible. Importing", length(sheetNames), "sheets."))
    
    #Number of plates/sheets to process
    chosenNumber <- as.integer(length(sheetNames))
    
  } else if(length(sheetNames) == nplate){
    
    chosenNumber <- as.integer(length(sheetNames))
    
  }
  
  if(alternate_start != 0){
    print(paste("User provided an alternate start plate. Sheet 1 will be plate",
                alternate_start))
    }
  
  #### Processing - Sheets ####
  #Create table to hold all the data.
  FinalTable <- data.frame()

  #Loop to go through the Excel sheets
  for(SN in 1:chosenNumber){
    
    if(alternate_start == 0){
    #To see that the code is running
    print(paste("Now processing sheet:", sheetNames[SN]))  
    } else {
    #To see that the code is running
    print(paste0("Now processing sheet '", sheetNames[SN],
                 "' as 'Plate ", alternate_start + SN-1, "'"))
    }
    
    
    
    #Read in data
    OriWorkbook <- read.xlsx(xlsxFile = filepath, sheet = sheetNames[SN], startRow = 1,
                             colNames = F, rowNames = F, detectDates = T,
                             skipEmptyRows = F, skipEmptyCols = F)
    
    #Convert all NAs into blanks
    OriWorkbook[is.na(OriWorkbook)] <- ""
    
    #Create clearer plate name values
    if(length(sheetNames) == 1 & sheetNames[1] == "Result sheet"){
      sheetNames[1] <- "Plate 1"
    }
    
    sheetNames_split <- str_split(sheetNames[SN], " ")
    
    if(alternate_start == 0){
    plateNumber <- as.integer(sheetNames_split[[1]][2])
    } else {
    plateNumber <- as.integer(sheetNames_split[[1]][2]) + alternate_start-1
    }
    
    #Locate the row with "Name" in the first column
    nameLocation <- which(OriWorkbook$X1 == "Name")
    
    #Locate the start positions of all tables indicated by the "<>"
    tableLocation <- which(OriWorkbook$X1 == "<>")
    
    #### Processing - Channels ####
    #Check if all channels actually exists in the sheet
    templist <- OriWorkbook$X2[nameLocation][OriWorkbook$X2[nameLocation] != ""]
    if(!any(channellist %in% templist)){stop("None of the channels exist within the sheet.")}
    
    newchannellist <- channellist[channellist %in% templist]
    
    for(CH in 1:length(newchannellist)){
      
      workingChannel <- newchannellist[CH]
      
      #To see that the code is running
      print(paste("Processing channel:", workingChannel))
      
      #Locate the row with channel name in the second column
      channelLocation <- which(OriWorkbook$X2 == workingChannel)
      
      #Locate the nearest table to the label that is below it (not above it)
      channeltableDiff <- tableLocation - channelLocation
      
      channeltableStart <- channelLocation + min(channeltableDiff[channeltableDiff > 0])
      
      #Time to subset out. Format is [row,col]
      channeltable1 <- OriWorkbook[((channeltableStart+1):(channeltableStart+32)),]
      colnames(channeltable1) <- OriWorkbook[((channeltableStart)),]
      
      #Change the column name for the row values from "<>"
      colnames(channeltable1)[1] <- "row"
      
      #Collapse into a long format
      channeltable2 <- pivot_longer(data = channeltable1, cols = 2:ncol(channeltable1),
                                    names_to = "col", values_to = workingChannel) %>%
        mutate(plate = paste(sprintf("p%02d", plateNumber))) %>%
        select(1:2,4,3)
      
      #channeltable2[,workingChannel] <- ifelse(channeltable2[,workingChannel] == "OVER", NA, channeltable2[,workingChannel])
      channeltable2[,4][channeltable2[,4] == "OVER"] <- NA
      
      if(CH == 1){
        
        #For first run, just assign the table
        channelTable <- channeltable2
        
      } else {
        
        #Then, subsequent runs will use left_join
        channelTable <- left_join(channelTable, channeltable2, by = c("row", "col", "plate"))
        
      }
    }
    
    FinalTable <- rbind(FinalTable, channelTable)
    
  }
  
  FinalTable <- FinalTable %>%
    mutate_at("col", as.integer) %>%
    mutate_at(4:ncol(.), as.integer) %>%
    mutate(well = paste0(row, sprintf("%02d", col)))

  FinalTable
}

#Function for converting phenobooth images from png to jpeg
convertImages_batch <- function(filedirectory_input, sourcePattern, filedirectory_output, all_files = T, crop_size = NULL){
  
  require(magick)
  
  #folders
  input_folder <- filedirectory_input
  output_folder <- filedirectory_output
  print(paste0("Input folder:", input_folder))
  print(paste0("Output folder:", output_folder))
  
  #files
  inputfilelist <- dir(input_folder, pattern = sourcePattern)
  #print(inputfilelist)
  outputfilelist <- dir(output_folder, pattern = ".jpeg")
  #print(outputfilelist)
  
  #Check if there is already files at the output folder with the expected same name.
  inputlist <- str_sub(inputfilelist, 1, -5)
  outputlist <- str_sub(outputfilelist, 1, -6)
  
  if(any(inputlist %in% outputlist)){
    message("WARNING. There are files in the output folder with very similar names.
            Proceeding with this function will overwrite files.")
    userCheck <- readline("Proceed? (T/F)")
    if(userCheck == "F" | userCheck == "f"){
      stop("User aborted run.")
    } else if(userCheck == "T" | userCheck == "t"){} else {
        stop("Unknown command. Exiting function.")}
  }
  
  #Crop sizes
  if(!is.null(crop_size)) {
    eff_crop_size <- crop_size
    print(paste0("Crop size is user defined as:", eff_crop_size))
  } else if(is.null(crop_size)) {
    print(paste0("No crop size defined. Running based on input image size."))
  }
  
  if(!all_files){
    
    print(inputfilelist)
    
    message("User wants to select specific files to convert.
            Please input file numbers desired separated by commas or as a vector.
            Example: 1,4,10 or c(2:7) or c(2:5,7,14:16)")
    selected <- readline("Input vector of numbers:")
    
    
    if(str_detect(selected, "c\\(") & str_detect(selected, "\\)")){
      #If the input has the format of "c( ... )", then do this.
      selected <- eval(parse(text = selected))
      
      } else if(!(str_detect(selected, "c\\(") & str_detect(selected, "\\)"))){
        #If the input is just a string of numbers without c(), eg. 1,4,7,15, this do this.
        selected <- as.numeric(unlist(strsplit(selected, "[[:punct:][:space:]]+")))
        
      } else {
        stop("Input format incorrect. Exiting function.")
      }
    
    #print((selected))
    #print(is.vector(selected))
    #print(inputfilelist[selected])
    #print(any(is.na(inputfilelist[selected])))
    
    if(is.vector(selected) & !any(is.na(inputfilelist[selected]))){
      inputfilelist <- inputfilelist[selected]
      message(paste0("User selected these files only:"))
      print(inputfilelist)
      
    } else if(!is.numeric(selected)){
      stop("Input is not a vector of numbers. Please provide only a vector of numbers.
           Exiting function.")
    } else if(!any(is.na(inputfilelist[selected]))){
      stop("Selection is out of bounds. Number for file selection is not within list of files.
           Exiting function.")
    }
  }

  #Do the conversion
  for (p in 1:length(inputfilelist)) {
    
    inputfilename <- paste(input_folder, inputfilelist[p], sep = "/")
    img <- image_read(path = inputfilename, strip = T)
    
    image_size_table <- image_info(img)
    if(is.null(crop_size)){
      image_width <- image_size_table$width
      image_height <- image_size_table$height
      print(paste("Input image has measurements of width x height:", image_width,"x", image_height))
      
      if(image_width == 2560 & image_height == 1920) {
        eff_crop_size <- "1480x990+530+420" #For 2560x1920
        
      } else if(image_width == 4128 & image_height == 3096) {
        eff_crop_size <- "2400x1600+850+680" #For 4128x3096
        
      } else {
        print(paste("Image size is not within pre-defined formats.",
                    "Please provide values for the crop size needed.",
                    "See ?image_crop.",
                    "Skipping file:", inputfilelist[p]))
      }
    }
    
    if(!is.null(eff_crop_size)) {
      img2 <- image_crop(img, eff_crop_size)
      img3 <- image_convert(img2, type = 'grayscale')
      img4 <- image_modulate(img3, brightness = 80)
      
      outputfilename <- paste0(paste(output_folder, str_sub(inputfilelist[p], 1, -5), sep = "/"), ".jpeg")
      image_write(image = img4, path = outputfilename, format = "jpeg", quality = 100)
    }
    
  }
  
  #Clear memory after opening and converting large files
  ## Maybe I have to move this into the loop above instead of at the end.
  gc(verbose = FALSE)
  
}

convertImages_single <- function(filedirectory_input, filename_input, filedirectory_output, crop_size = NULL){
  
  require(magick)
  
  #folders
  input_folder <- filedirectory_input
  output_folder <- filedirectory_output
  print(paste0("Input folder:", input_folder))
  print(paste0("Output folder:", output_folder))
  
  #files
  outputfilelist <- dir(output_folder, pattern = ".jpeg")
  
  #Check if there is already files at the output folder with the expected same name.
  inputlist <- str_sub(filename_input, 1, -5)
  outputlist <- str_sub(outputfilelist, 1, -6)
  
  if(any(inputlist %in% outputlist)){
    message("WARNING. There are files in the output folder with very similar names.
            Proceeding with this function will overwrite files.")
    userCheck <- readline("Proceed? (T/F)")
    if(userCheck == "F" | userCheck == "f"){
      stop("User aborted run.")
    } else if(userCheck == "T" | userCheck == "t"){} else {
        stop("Unknown command. Exiting function.")}
  }
  
  #Crop sizes
  if(!is.null(crop_size)) {
    eff_crop_size <- crop_size
    print(paste0("Crop size is user defined as:", eff_crop_size))
  } else if(is.null(crop_size)) {
    print(paste0("No crop size defined. Running based on input image size."))
  }

  #Do the conversion
  inputfilename <- paste(input_folder, filename_input, sep = "/")
  img <- image_read(path = inputfilename, strip = T)
  
  image_size_table <- image_info(img)
  if(is.null(crop_size)){
    image_width <- image_size_table$width
    image_height <- image_size_table$height
    print(paste("Input image has measurements of width x height:", image_width,"x", image_height))
    
    if(image_width == 2560 & image_height == 1920) {
      eff_crop_size <- "1480x990+530+420" #For 2560x1920
      
    } else if(image_width == 4128 & image_height == 3096) {
      eff_crop_size <- "2400x1600+850+680" #For 4128x3096
      
    } else {
      gc(verbose = FALSE)
      stop(paste("Image size is not within pre-defined formats.",
                  "Please provide values for the crop size needed.",
                  "See ?image_crop.",
                  "Skipping file:", filename_input))
    }
  }
  
  img2 <- image_crop(img, eff_crop_size)
  img3 <- image_convert(img2, type = 'grayscale')
  img4 <- image_modulate(img3, brightness = 80)
  
  outputfilename <- paste0(paste(output_folder, str_sub(filename_input, 1, -5), sep = "/"), ".jpeg")
  image_write(image = img4, path = outputfilename, format = "jpeg", quality = 100)
  
  
  #Clear memory after opening and converting large files
  ## Maybe I have to move this into the loop above instead of at the end.
  gc(verbose = FALSE)
  
}

```

This document contains the workflow for read-in of data from TECAN measurements and phenobooth images of the mNG-AID*-3Myc experiment performed with the mNG-tagged (mNeonGreen) strains. The data is checked for any plate shift effects. Then, the data is transformed to use the high-gain measurements.

The workflow should be:


# Image data

## Photograph Segmentation

```{r photoseg, include = FALSE, eval = FALSE}
## Segment Imaging plates photographs ####
raw_img_folder_Img <- paste(PrimaryDirectory, raw_img_folder, "Images", sep = "/")
analysis_folder_Img <- paste(PrimaryDirectory, analysis_folder, "Images", sep = "/")

convertImages_batch(filedirectory_input = raw_img_folder_Img,
                    sourcePattern = ".png",
                    filedirectory_output = analysis_folder_Img)

#head(dir(analysis_folder_Img, pattern=".jpeg"))
setwd(analysis_folder_Img)
gitter.batch(analysis_folder_Img, plate.format=1536, verbose="p",
             grid.save=analysis_folder_Img, dat.save=analysis_folder_Img)

#setwd(analysis_folder_Img)
nPlates <- 96
photoNamesImg <- dir(analysis_folder_Img, pattern = "jpeg.dat")
photoDataImg <- data.frame()
for (i in 1:nPlates) {
  photoImg <- gitter.read(photoNamesImg[i]) %>%
    mutate(row1536=alphabet1536[row], plate=paste(sprintf("p%02d", i)))
  photoDataImg <- bind_rows(photoDataImg, photoImg)
}
names(photoDataImg)[3:4] <- c("sizeImg","circularityImg")
#photoDataImg <- photoDataImg %>%
setwd(PrimaryDirectory)
save(photoDataImg, file = "photoData_Img.rda")

load("photoData_Img.rda")

```

## Measurement Data Read-In

```{r OE data read-in, include = FALSE, eval = FALSE}
#Data location
tempfilelist <- dir(raw_xlsx_folder, pattern = ".xlsx")
tempfilelist

#I have several files due to stacker issue and different measurement dates/timepoints
rename_list <- paste0("df", str_sub(tempfilelist, 16, -6))
rename_list

df_all <- data.frame()
for(n in 1:length(tempfilelist)){
  df_temp <- Read_Screen_Data(filename = tempfilelist[n],
                              filedirectory = raw_xlsx_folder,
                              channels = c("mNG_lo", "mNG_hi"),
                              nplate = 1)%>%

  mutate(plate=paste(sprintf("p%02d", n))) #Necessary to give the right name to the plates
  df_all <- rbind(df_all, df_temp)
  


  assign(rename_list[n], df_temp)

  rm(df_temp)
}

str(df_all)

save(df_all, file = "rawScreenDataTable.rda")

```


```{r OE append annotation and photodata, include = FALSE, eval = FALSE}
#Load necessary values and data if reset/not continuous
load("rawScreenDataTable.rda")

# Combine data frame with photodata
load("photoData_Img.rda")


photoDataImg$well <- paste0(photoDataImg$row1536, sprintf("%02d", photoDataImg$col))


df1 <- left_join(df_all, photoDataImg %>%
                   select(sizeImg, circularityImg, plate, well),
                 by = c("plate", "well"))


# Combine data frame with annotation file
df3 <- left_join(mNG_AID_anno, df1, by = c("plate", "well"))

save(df3, file = "dataTableRaw.rda")

```


CHECK WITH JOHN


```{r OE plateshift check, include = FALSE, eval = FALSE}
# Filtering border colonies
df_noBorder <- anti_join(df3, BorderColonies)

# Plotting the plateshift boxplot
dfplateShift_wBorder <- df3 %>% filter(sample_type == "sample")
dfplateShift_NoBorder <- df_noBorder %>% filter(sample_type == "sample")

plateShift <- grid.arrange(
  ggplot(dfplateShift_wBorder, aes(as.factor(plate_1536), log2(mNG_lo))) +
    geom_boxplot(fill = "darkgreen") +
    labs(x = "mNG",
         y = "log2(mNG)", title = "WT fluorescence level with Border colonies") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)),
  ggplot(dfplateShift_NoBorder, aes(as.factor(plate_1536), log2(mNG_lo))) +
    geom_boxplot(fill = "darkgreen") +
    labs(x = "mNG",
         y = "log2(mNG)", title = "WT fluorescence level without Border colonies") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)),
  nrow = 2)
plot(plateShift)

ggsave(filename = paste((format(Sys.time(), "%Y%m%d_%H%M")), "_ShiftedPlates_All.pdf", sep = ""), 
       plot = plateShift, device = "pdf", dpi = "retina",
       path = paste(PrimaryDirectory, plots_folder, sep = "/"), height=28, width=25, units="in")

plateSd_wBorder <- dfplateShift_wBorder %>%  
  summarize(plateSd=sd(log2(mNG_lo), na.rm=TRUE)) %>%
  ungroup() %>%
  arrange(desc(plateSd))

plateSd_NoBorder <- dfplateShift_NoBorder %>% 
  summarize(plateSd=sd(log2(mNG_lo), na.rm=TRUE)) %>%
  ungroup() %>%
  arrange(desc(plateSd))

plateSd_wBorder
plateSd_NoBorder

```

### OE Gain adjustment

```{r OE Adjusting data for high gain use, include = FALSE, eval = FALSE}
#Joining and rearranging columns
df_HiLo <- df3
colnames(df_HiLo)[30:31] <- c('mNGLo','mNGHi')

#Calculating the ratio between High and Low gains
#df_HiLo$mCherry <-(df_HiLo$mCherryHi/df_HiLo$mCherryLo)
df_HiLo$mNG <-(df_HiLo$mNGHi/df_HiLo$mNGLo)

#Check to see if there are any where there is not even a value for the low gain
#Should be 0 obs.
#checkred <- subset(df_HiLo, is.na(mCherry) & is.na(mCherryLo))
checkgreen <- subset(df_HiLo, is.na(mNG) & is.na(mNGLo))

#Did a quick check to see if any of the true strains have NA values for the high gain.
colonyquickcheck <- df_HiLo %>% anti_join(., BorderColonies) %>%
  filter(ORF != "BORDER") %>%
  summarise(NA_Check_mNG = is.na(median(mNG)))
#From the table above, for mNG signal, all true strains were measured at high gain including reference strains.


#The plots below illustrate another issue that the gain ratio calculation for some plates were not similar to the rest
#grid.arrange(
#  ggplot(df_HiLo %>% anti_join(., BorderColonies) %>%
#           filter(ORF != "BORDER"), aes(paste(IncTemp, Rep, carbonsource, Day, Notes, sep = "_"), mCherry)) +
#    geom_boxplot(fill = "red") + #geom_jitter() +
#    labs(x = "Plate", y = "mCH", title = "All border colonies removed") +
#    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  ,
  ggplot(df_HiLo %>% anti_join(., BorderColonies) %>%
           filter(ORF != "BORDER"), aes(as.factor(plate_1536),mNG)) +
    geom_boxplot(fill = "darkgreen") + #geom_jitter() +
    labs(x = "Plate", y = "mNG", title = "All border colonies removed") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  ,
  nrow = 2)


grid.arrange(
  ggplot(df_HiLo %>% anti_join(., BorderColonies) %>%
    filter(ORF != "BORDER"), 
   aes(as.factor(plate_1536),log10(mNGLo))) +
      geom_boxplot(fill = "darkgreen") + geom_hline(yintercept = 2, col = "blue", size = 1.5, lty = 2) +
      labs(x = "Plate", y = "mNGLo", title = "All border colonies removed") +
    scale_y_continuous(limits = c(1,5), breaks = seq(0,5,1)) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
  ,
  ggplot(df_HiLo %>% anti_join(., BorderColonies) %>%
    filter(ORF != "BORDER"), aes(as.factor(plate_1536),log10(mNGHi))) +
      geom_boxplot(fill = "darkgreen") + geom_hline(yintercept = 2, col = "blue", size = 1.5, lty = 2) +
      labs(x = "Plate", y = "mNGHi", title = "All border colonies removed") +
    scale_y_continuous(limits = c(1,5), breaks = seq(0,5,1)) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
  , nrow = 2)

#While probably it is the best that no gain adjustment is done.
# The codes below does not adjust the positions that already have a high gain reading so it also does not affect much of the values measured.


#Calculating the SD, mean and median for HiLo-ratio of red and green signals
#Check to make sure the median and mean are not too different
# sdred <- round(sd(df_HiLo$mCherry, na.rm=T), digits=4)
# avgred <- round(mean(df_HiLo$mCherry, na.rm=T), digits=4)
# medred <- round(median(df_HiLo$mCherry, na.rm=T), digits=4)

sdgreen <- round(sd(df_HiLo$mNG, na.rm=T), digits=4)
avggreen <- round(mean(df_HiLo$mNG, na.rm=T), digits=4)
medgreen <- round(median(df_HiLo$mNG, na.rm=T), digits=4)


# paste0("mCherry: ","SD=",sdred," | Mean=",avgred," | Median=",medred)
paste0("mNG: ","SD=",sdgreen," | Mean=",avggreen," | Median=",medgreen)

#Creating backup
df_HiLoORI <- df_HiLo #as backup
df_HiLo <- df_HiLoORI #to revert

#Using the ratio to calculate high gain values for all observations
df_HiLo <- df_HiLo %>%
  mutate(#mCherry = ifelse(is.na(mCherry), mCherryLo*medred, mCherryHi),
         mNG = ifelse(is.na(mNG), mNGLo*medgreen, mNGHi))

#To check if correctly done, should not see blue at lower intensities, but only purple (blue+red)
#It is possible to have a blue tail at the higher intensities where a lot of high gain values were missing(NA)
ggplot(data=df_HiLo) + geom_histogram(aes(log10(mNG)), bins=100, fill="blue", alpha=0.9) + 
  geom_histogram(aes(log10(mNGHi)), bins=100, fill="red", alpha=0.5)

#Removing the individual high and low gain columns 
df <- df_HiLo %>%
  select(-mNGLo,-mNGHi)

save(df, file = "dataTableRaw_GainAdj.rda")

```

# R Studio Session Info

```{r Session info}
sessionInfo()

```